#Course Project 2

##Reading and viewing data.
```{r, cache=TRUE}
data  <- readRDS("./summarySCC_PM25.rds")
dataSCC  <- readRDS("./Source_Classification_Code.rds")
```

##Question 1
Here we will plot the decreasing of the USA PM2.5 emmissions from 1999 to 2008.
If you'd like to have this picture on your local computer, just del the comment sharp symbol and run the code. 
```{r}
library(dplyr)
summary  <- data %>%
    group_by(year) %>%
    summarise(emissions = sum(Emissions))
#png(filename = "plot1.png", width = 480, height = 480, units = "px", bg = "transparent")
with(summary, barplot(emissions, year, ylim = c(0, max(emissions)), ylab = "Emissions (tons)",
                      names.arg = year, xlab = "Year", main = "Total emissions from PM2.5"))
#dev.off()
```

##Question 2
The same as the first, but with specified location - **Baltimore City**(fips == "24510")
```{r}
summary  <- data[data$fips == "24510",] %>%
    group_by(year) %>%
    summarise(emissions = sum(Emissions))
#png(filename = "plot2.png", width = 480, height = 480, units = "px", bg = "transparent")
with(summary, barplot(emissions, year, ylim = c(0, max(emissions)), ylab = "Emissions (tons)",
                      names.arg = year, xlab = "Year", main = "Total emissions from PM2.5 in Baltimore City"))
#dev.off()
```

##Question 3
Increases and decreases of the emissions by the **type** (point, nonpoint, onroad, nonroad) variable.
```{r}
library(ggplot2)
data$type  <- as.factor(data$type)
summary  <- data[data$fips == "24510",] %>%
    group_by(year, type) %>%
    summarise(emissions = sum(Emissions))
#png(filename = "plot3.png", width = 480, height = 480, units = "px", bg = "transparent")
ggplot(data = summary, aes(x = year, y = emissions, col = type, fill = type))+
    geom_line()+
    geom_point()+
    xlab("Year")+
    ylab("Emissions (tons)")+
    ggtitle("PM2.5 emissions in Baltimore City by the source type")
#dev.off()
```

##Question 4
Emissions from coal combusion-related sources.
```{r}
library(data.table)
data$Pollutant  <- as.factor(data$Pollutant)
data$year  <-  as.factor(data$year)
#dataCoalSCC  <- dataSCC[dataSCC$EI.Sector %like% "Coal",]
dataCoalSCC  <- filter(dataSCC, SCC.Level.One %like% "Comb", EI.Sector %like% "Coal")
dataCoal  <- data[data$SCC %in% dataCoalSCC$SCC,]
summary  <- dataCoal %>%
    group_by(year) %>%
    summarise(emissions = sum(Emissions))
#png(filename = "plot4.png", width = 480, height = 480, units = "px", bg = "transparent")
ggplot(data = summary, aes(x = year, y = emissions))+
    geom_bar(stat = "identity", width = .7, fill = "light blue", col = "Black")+
    xlab("Year") + ylab("Emissions (tons)") + ggtitle("PM2.5 emissions from coal combusion-related sources in USA")
#dev.off()
```

##Question 5
Changes from motor vehicle sources from 1999-2008 in **Baltimore City**
```{r}
dataVehiclesSCC  <- filter(dataSCC, EI.Sector %like% "Vehicles")
dataVehicles  <- data[data$SCC %in% dataVehiclesSCC$SCC,]
summary  <- dataVehicles[dataVehicles$fips == "24510",] %>%
    group_by(year) %>%
    summarise(emissions = sum(Emissions))
#png(filename = "plot5.png", width = 480, height = 480, units = "px", bg = "transparent")
ggplot(data = summary, aes(x = year, y = emissions))+
    geom_bar(stat = "identity", width = .7, fill = "light blue", col = "Black")+
    xlab("Year") + ylab("Emissions (tons)") + ggtitle("PM2.5 emissions from motor vehicle sources in Baltimore City, USA")
#dev.off()
```

##Question 6
Comparing the **Los Angeles County** with **Baltimore City** by the emmissions amounth.
```{r}
summary  <- dataVehicles[dataVehicles$fips %in% c("24510", "06037"),] %>%
    group_by(year, fips) %>%
    summarise(emissions = sum(Emissions))
summary  <- mutate(summary, Location = ifelse(fips == "24510", "Baltimore City", "Los Angeles County"))
#png(filename = "plot6.png", width = 480, height = 480, units = "px", bg = "transparent")
ggplot(data = summary, aes(x = year, y = emissions, col = Location, group = Location))+
    geom_line() +
    geom_point() +
    xlab("Year") + 
    ylab("Emissions (tons)") + 
    ggtitle("PM2.5 emissions from motor vehicle sources in USA")
#dev.off()
```